\begin{abstract}
   
   Currently, Stellenbosch University only has cash-based vending machines
   available. This means that a physical cash transaction has to take place before the vending machine can
   dispense its products. In a world moving away from using cash, this payment
   approach becomes a problem since less people are likely to carry around cash
   on their person. Therefore, it is important that vendors and manufacturers
   keep up with the trend and implement the latest technologies in their
   products and payment methodologies.
   
   This project focused on introducing a vending machine system that will allow
   customers to pay for their products using only their cellphones. The project was designed
   to use existing technologies, services and protocols wherever possible. The system is
   based mainly on the Python programming language, with some Java code
   implemented in the Android application.
   
   The two main technologies implemented are Quick Response Codes (QR Codes) and Near
   Field Communication (NFC). An Android application was created to facilitate payments
   made via NFC. A cloud-based server was also created and is used by the vending machine
   and Android application to validate transactions. To demonstrate that the
   system works, a model vending machine was designed and built that uses the cashless
   payment system.
   
   The results of this project are favourable and show that it is possible to make a
   cashless vending machine. However, more work still needs to be done to fully
   commercialise and optimise this system and make it more user friendly. 
   
\end{abstract}

\endinput
