\chapter{Asymmetric Encryption}
\label{app:ass-encryption}

Asymmetric encryption is most easily explained with a postal analogy:

Imagine that two people, Alice and Bob, want to send each other secret messages through
the public mail. In other words, Alice wants to send Bob a secret message and she expects
a secret reply from Bob, and vice versa. 

In an asymmetric scheme, Bob can lock his letter to Alice with a padlock to which only she has
a key (she keeps this on her person at all times and does not show it to anyone, which
includes Bob). This open padlock represents the public key half of Alice's key. This
means that anyone can send Alice a secure message with a public key, which is easy to
get from Alice, and only Alice can unlock the message with her private key half of the
key pair. Similarly, Alice can lock her letter with Bob's padlock which only Bob can open.

The great advantage that this has over symmetric encryption is that the decryption keys never
have to be exchanged between parties. This neutralises the risk of a middle-man attack,
analogous to a nosy postal worker called Eve who likes to read other people's
mail, who then intercepts the message and steals the key. Also, if for example Bob has
been careless and allowed Eve to see his key, his messages to Alice will be
compromised. However, the messages from anyone else (including Bob) to Alice
will remain as secure as it was before Bob lost his key.

The data source can also be signed and verified by using this key scheme. Referring once again
to the postal analogy: To show Alice that it was indeed Bob who sent her the
message, and not Eve for example, he can send an extra message along with the
original message. This extra message is locked with Bob's key that he shares
with no one (i.e. his private key). However, Bob has sent out his public key to
everyone who wants it. These keys can \emph{only} be used to unlock the
messages locked with Bob's own private key. Therefore, if Alice, who received
one of Bob's keys, can unlock this extra message with that key, she knows that
as long as Bob has not given anyone his private key, it can only be his
message. The reverse is also true if Alice wants to prove to Bob that it was
indeed she who sent him a message.