%*** Summary Heading ************************************************

\begin{Summary}{Mechatronic Project 488: Summary}

   \noindent
   \begin{tabular}{@{}ll@{}}
      \textsf{Student:}  &  JC\ Lock\\
      \textsf{Co-worker:} & N/A
   \end{tabular}

%*** The Summary table **********************************************
\begin{SumTable}
 \hline%=============================================================
 \SumHead{Title of Project}\\
 \hline%=============================================================
 Development of a Cashless Vending Machine.
 \\

 \hline%=============================================================
 \SumHead{Objectives}\\
 \hline%=============================================================
 Program and build a model vending machine which accepts payments made via a cellphone.
 \\

 \hline%=============================================================
 \SumHead{Which aspects of the project are new/unique?}\\
 \hline%=============================================================
 The use of simple cellphone technologies which most students currently have built
 into in their cellphones, such as NFC and QR Codes.
 \\
   
 \hline%=============================================================
 \SumHead{What are the findings?}\\
 \hline%=============================================================
 A working test model was built which accepts faux money paid with either QR Codes or NFC. All
 the necessary security measures, i.e. encryption and challenge codes, were added as well as a
 central web server that tracks user transactions.
 \\

 \hline%=============================================================
 \SumHead{What value do the results have?}\\
 \hline%=============================================================
 The results show that the machine is working reliably. Some improvements can be made, but
 overall the vending machine is working as expected.
 \\

 \hline%=============================================================
 \SumHead{If more than one student is involved, what is each one's contribution?}\\
 \hline%=============================================================
 Only one student was involved in this project.
 \\

 \hline%=============================================================
 \SumHead{Which aspects of the project will carry on after completion?}\\
 \hline%=============================================================
 This project has been successfully completed and will therefore not continue.
 \\

 \hline%=============================================================
 \SumHead{What are the expected advantages of continuation?}\\
 \hline%=============================================================
 N/A
 \\

 \hline%=============================================================
 \SumHead{What arrangements have been made to expedite continuation?}\\
 \hline%=============================================================
 N/A
 \\

 \hline%=============================================================
\end{SumTable}

%*** Signatures *****************************************************

\vspace{1.5cm}
\SumSignatures

\end{Summary}

\endinput
